Template for indicator documentation

### 2023-03-13 slitasje.Rmd
try to warp

There is some, but very little variation, both between the ecosystems
and between the four HIF classes in the modified infrastructure index.
Note however, that for wetland and semi-natural areas we did not
extrapolate values for the most urban areas, and that for naturally open
areas we did not extrapolate to the least affected areas.

@@

-   indicator maps (vector data), and we have

-   total HIA areas, and we have the

-   extrapolated indicator maps (HIA maps with aggregated indicator
    values and errors, also vector data).

@@

```{r, eval=F}
mireET <- sf::st_read("/data/R/Kladd/Myr/Myrmodell.gdb")
```

This doesn't take that long.

```{r, eval=F}
mireET <- st_transform(mireET, 25833)
```

This take about 10 min. Not sure I need it.

```{r, eval=F}
mireET <- st_make_valid(mireET)
```

This takes a long!! time, and should be AVOIDED.

```{r, eval=F}
wetlands_slitasje_extr_cropped <- sf::st_intersection(wetlands_slitasje_extr, mireET)
```

Instead I will draw some random point samples.

>>>>

Note that for wetland and semi-natural areas we did not
extrapolate values for the most urban areas, and that for naturally open
areas we did not extrapolate to the least affected areas.
For the other regions we generally excluded more HIFs.

@@

-   indicator maps (vector data, small polygons), and we have

-   total area for each HIA class and region combo, and we have the

-   extrapolated indicator maps (HIA maps with aggregated indicator
    values and errors, also vector data, wall-to-wall with some NA areas).

@@

```{r, eval=F}
#takes about one minute
mireET <- stars::read_stars("/data/P-Prosjekter2/41201785_okologisk_tilstand_2022_2023/data/Myrmodell/myrmodell90pros.tif",
                             proxy=F)
```

This is in the wrong CRS.

```{r}
mireET <- sf::st_transform(mireET, 25833)
```

```{r, eval=F}
system.time(
  mireET_warped <- stars::st_warp(mireET, grid)
)
```

user: 597.308

system: 139.164

elapsed: 735.907

```{r}
mireET
```

```{r, eval=F}
write_stars(mireET_warped, paste0(pData, "wetland_ecosystem_EPSG25833_50m.tif"))
```

```{r}
wetlands_trd <- sf::st_crop(mireET, myBB)
tm_shape(wetlands_trd)+
  tm_raster()+
  tm_shape(hw_utm)+
  tm_lines(col="blue")
```

## OLD
Instead I will draw some random point samples.
